%% Marco Sgobino
%% Tesi di laurea triennale
% file-bibliografia.tex
\titleformat{\chapter}[display]
{\Huge\bfseries}{}{0pt}{}
\clearpage
\addcontentsline{toc}{chapter}{Bibliografia}
\begin{thebibliography}{9}
        \bibitem{opentx-website} OpenTX, \underline{https://www.open-tx.org/}, 2014.
        \bibitem{opentx-radios} OpenTX, \underline{https://www.open-tx.org/radios}, 2014.
        \bibitem{opentx-github} Repository OpenTX su GitHub, \underline{https://github.com/opentx/opentx}, 2021.
        \bibitem{oss-osh-uavs} Burdziakowski, P., Razmjooy, N., Estrela, V., \& Hemanath, J. (2020). \emph{``Open-source software (OSS) and hardware (OSH) in UAVs''}. 49-66
        \bibitem{mission-planner-website} ArduPilot Dev Team, \underline{https://ardupilot.org/planner/}, 2021.
        \bibitem{ardupilot-website} ArduPilot, \underline{https://ardupilot.org/}, 2016.
        \bibitem{opendronemap} OpenDroneMap Authors ODM, \emph{``A command line toolkit to generate maps, point clouds, 3D models and DEMs from drone, balloon or kite images.''} \underline{https://github.com/OpenDroneMap/ODM}, 2020.
        \bibitem{webodm-website} UAV4GEO, \underline{https://webodm.net/}.
        \bibitem{rise-uavs} Cummings, Anthony R.; McKee, Arlo; Kulkarni, Keyur; Markandey, Nakul, \emph{``The Rise of UAVs''}, Photogrammetric Engineering \& Remote Sensing, Volume 83, Number 4, April 2017, pp. 317-325(9)
        \bibitem{italy-uavs} Andrea Cardamone, \emph{``Implementation of a pilot in the loop simulation environment for UAV development and testing''}, \underline{http://hdl.handle.net/10589/135202} 2017.
        \bibitem{opentx-firmware} OpenTXU, \underline{http://open-txu.org/home/undergraduate-courses/introduction/how-rc-works/}, 2014.
        \bibitem{opentx-lua-instructions} OpenTX, \underline{https://www.open-tx.org/lua-instructions.html}, 2014.
        \bibitem{lua-website} Lua Project, \underline{https://www.lua.org/}, 2020.
        \bibitem{opentx-companion-manual} OpenTX, \underline{https://doc.open-tx.org/manual-for-opentx-2-2/companion}.
        \bibitem{fedora-website} Fedora Project, \underline{https://getfedora.org/}, 2021.
        \bibitem{opentx-download-page} OpenTX, \underline{https://www.open-tx.org/downloads}, 2014.
\end{thebibliography}

% https://www.ingentaconnect.com/content/asprs/pers/2017/00000083/00000004/art00016#
% https://mostwiedzy.pl/pl/publication/open-source-software-oss-and-hardware-osh-in-uavs,152706-1
% https://www.politesi.polimi.it/handle/10589/135202?mode=complete
